An Invariant Framework for Conducting Reproducible Computational Science

### 2015-03-18 intro.tex
Remove unused stuff

% Reproducibility
Reproducibility is a cornerstone of the scientific method~\cite{borgman2012data}. 
Its importance is underscored by its ability to advance science---reproducing by verifying and validating a scientific result leads to improved understanding, thus increasing possibilities of reusing or extending the result. 
Ensuring reproducibility of a scientific result, however, often entails detailed documentation and specification of the involved scientific method. Historically, this has been achieved through text and proofs in a publication. 
As computation pervades the sciences and transforms the scientific method, mere text is considered insufficient. 
In particular, apart from textual descriptions describing the result, a reproducible result must also include several computational artifacts, such as software, data,  environment variables, and state of computation that are involved in the adopted scientific method \cite{Sole}.

@@

Since reproducibility is significantly about comprehensive documentation, virtualization approaches in their current form only make it easy to capture the computations. Preserving the computations, so that they are easy to understand, install, or alter implicit dependencies that are part of computation, especially as dependencies and software components evolve or become deprecated, is not effectively addressed. There are two approaches to address the preservation challenge. By either introducing tools that help document dependencies and provide software attribution within VMIs or packages, or alternatively by using software delivery mechanisms, such as, centralized package management, Linux containers, and the, more recent, Docker framework. We examined the first approach previously in \cite{SoftProv}. 
In this paper we examine the second approach. 
In particular, we consider the light-weight virtualization approaches, because, we believe that the combination of light-weight approaches with more standardized software delivery mechanisms can lead to addressing the reproducibility challenge for a wide variety of scientific researchers. 
A package created by those light-weight approaches encapsulates all the necessary dependencies of an application, and can be used to repeat the application through different sandbox mechanisms, including Parrot, CDE, PTU, chroot, and Docker.
% they may help the This  We that must also include effective  to deliver the software to a wide audience. We examine the fire
%have recently emerged  several of the reproducible challenges that arise due to use of virtualization approaches.

@@

% For later. 
%The combination imposes additional overhead due to double virtualization, but saves on context switches, since every system call is not interposed.

\if 0
The rest of the paper is organized as follows. Section \ref{} describes the high energy physics application and the challenges involved in reproducing it. 
Section \ref{} describes the light-weight virtualization and software delivery mechanisms, such as linux containers and dockers. 
In Section \ref{} we describe the combined invariant framework, consisting of capture and preservation phases. 
Section \ref{} describes how to employ capture, preserve, and distribute phases to reproduce the high-energy physics application.
Section \ref{} provides the experimental results. Finally, we conclude in Section \ref{}. 
\fi

%-----
%OLD TEXT
%
%Reproducibility is a cornerstone of the scientific process~\cite{borgman2012data}.
%In order to understand, verify, and build upon previous work,
%one must be able to first recreate previous results by applying
%the same methods. Historically, reproducibility has been
%accomplished through painstaking detailed documentation recorded
%in lab notebooks, which are then summarized in peer-reviewed publications.
%But as science increasingly depends on computation,
%reproducibility must also encompass the environments, data, and software
%involved in each result~\cite{zabolitzky2002preserving}. It is widely recognized that informal
%descriptions of software and systems -- although common -- are insufficient
%for reproducing a computational result accurately.
%A more automated and comprehensive approach is required.
%
%The reproduction of a computation has three broad components,
%each of which suggests somewhat different approaches:
%
%\begin{itemize}
%\item The {\bf computing environment}, consisting of the basic hardware and the operating system which can be preserved as physical artifacts or as a combination of virtual machine monitors (hardware) and virtual machine images (operating system)~\cite{matthews2009towards}.
%\item The {\bf scientific data} to be analyzed has historically received the most attention for curation.  In a large, well-organized project, it may be stored in a  data repository or database management system, with associated documentation and a curation strategy.  In a small effort, it could simply be a handful of files.
%\item The {\bf software environment} includes the source code, binaries, scripts, configuration files, and everything else needed to execute the desired code.  As with data, the software could be drawn from a well-managed software repository, or it could be a handful custom scripts that exist in the user's home directory.
%\end{itemize}
%
%In a very abstract sense, reproducing a computation is trivial.
%Assuming a computation is deterministic, one must simply
%preserve all of the inputs to a computation, then re-run
%the same code in an equivalent environment, and the same result
%will be produced.  For a small custom application on a modest
%amount of data, this could be accomplished by capturing the
%complete environment,
%data, and software within a single virtual machine image,
%and then depositing the virtual
%image into a curated environment.  The publication could
%then simply refer to the identifier of the image, which the
%interested reader can obtain and re-use. This approach has
%been used to some success with systems~\cite{castagne2013consider}.
%\footnote{Of course, we are glossing over the problem that hardware
%architectures and virtual machines also change, so one must also
%preserve the VMM software necessary to run the image.  The VMM itself
%depends on a software environment which must also be preserved.
%A long-term preservation system might end up running a whole
%stack of nested virtual machines in order to provide the desired
%environment! }
%
%However, this simple approach is not sufficient for large applications
%that are run in complex environments.
%
%\begin{itemize}
%\item There may be {\bf implicit dependencies} on items that are
%not apparent to the end user.  For example, they may understand that
%they rely on a particular data analysis package, but would have
%no reason to know that the package has further dependencies on
%other libraries and configuration files.  Or, they may know that
%the computation only runs correctly on a particular machine, but
%not know this is because it relies on a filesystem that
%is mounted only on that machine.
%
%\item The {\bf granularity} of the dependencies may not be well understood.
%For example, the user may understand that a computation depends upon
%a data collection that is 1TB in overall size, but not have detailed
%knowledge that it only requires three files totalling 300MB out of that
%whole collection.
%
%\item There may be dependencies upon {\bf networked resources} that
%are inherently external to the system, such as a database, a code
%repository~\cite{cms2006cmssw}, or a scalable filesystem~\cite{blomer2011cernvm}.  For such resources, it
%must be decided whether the dependency will simply be noted, or if it
%must be incorporated whole or in part.
%
%\item Where {\bf common dependencies} are widely used, it may be inefficient or
%impossible to store one copy of each dependency for each archived object.
%Some form of sharing or de-duplication is necessary in order to keep
%the archive to a reasonable size.
%\end{itemize}
%
%We do not claim to have solved these problems in any comprehensive
%way.  Rather, our aim in this paper is to highlight the scope
%of the problems by presenting a case study of one complex application.
%The application is presented to us
%first in the form of an email that describes in prose how to install
%the software and run the analysis.  We perform several successive
%refinements to convert it into an executable and preservable object.
%We then develop techniques for reducing the size of the dependencies
%that are necessary for the object to function, and we demonstrate
%the preserved object functioning correctly in three different
%physical and cloud environments.
%We describe how each of these techniques may interact with
%a future archive of preserved software artifacts, and conclude with
%some reflections on the challenges of preservation and advice for future efforts.

>>>>

Reproducibility is a cornerstone of the scientific method~\cite{borgman2012data}. 
Its importance is underscored by its ability to advance science---reproducing by verifying and validating a scientific result leads to improved understanding, thus increasing possibilities of reusing or extending the result. 
Ensuring reproducibility of a scientific result, however, often entails detailed documentation and specification of the involved scientific method. Historically, this has been achieved through text and proofs in a publication. 
As computation pervades the sciences and transforms the scientific method, mere text is considered insufficient. 
In particular, apart from textual descriptions describing the result, a reproducible result must also include several computational artifacts, such as software, data,  environment variables, and state of computation that are involved in the adopted scientific method \cite{Sole}.

@@

Since reproducibility is significantly about comprehensive documentation, virtualization approaches in their current form only make it easy to capture the computations. Preserving the computations, so that they are easy to understand, install, or alter implicit dependencies that are part of computation, especially as dependencies and software components evolve or become deprecated, is not effectively addressed. There are two approaches to address the preservation challenge. By either introducing tools that help document dependencies and provide software attribution within VMIs or packages, or alternatively by using software delivery mechanisms, such as, centralized package management, Linux containers, and the, more recent, Docker framework. We examined the first approach previously in \cite{SoftProv}. 
In this paper we examine the second approach. 
In particular, we consider the light-weight virtualization approaches, because, we believe that the combination of light-weight approaches with more standardized software delivery mechanisms can lead to addressing the reproducibility challenge for a wide variety of scientific researchers. 
A package created by those light-weight approaches encapsulates all the necessary dependencies of an application, and can be used to repeat the application through different sandbox mechanisms, including Parrot, CDE, PTU, chroot, and Docker.

@@

### 2015-03-18 observation.tex
Remove unused stuff

%\comment{Although this starting point may seem extreme, it is
%perfectly natural for collaborators to share configurations
%with each other in this form, and to rely on the presence
%of a working environment with appropriate dependencies already
%installed.  From this starting point, the authors played the
%role of curators, whose job it is to prepare the application
%for permanent archival.
%
%First, we elaborated the email instructions into an
%executable script that obtains the dependencies and then
%executes the analysis.  The script declares the necessary
%environment variables, downloads and checks out the necessary source code,
%builds it appropriately, calls initialization scripts in
%the dependent software, and then runs the analysis.
%A few rounds of correction with the original author were necessary
%to obtain all the dependencies and run the artifact correctly.
%(The original instructions introduced in the email also indicated how to run the application
%within a production batch system.  For the purposes of preservation,
%we consider the execution infrastructure to be distinct from the application,
%and leave it out of consideration for now.)
%
%The process of elaborating the program into a script revealed
%several observations about this type of application:}

@@

%networked external resources. 
%Capturing these dependencies is straightforward if they are static in nature and the resources can be accessed without secure cryptographic functions. 
%For instance, in TauRaoast some source code external dependencies can be obtained by simply downloading the specific libraries from a web page. 
%However, other static dependencies require making secure connections to Github resources, and CVS servers for downloading source. 
%While TauRoast is completely local in its execution, dynamic remote dependencies that arise in a distributed execution 
%
%The application data and code is distributed on five networked filesystems, which are 
%typically mounted on a particular machine that is made accessible to the application developer. In TauRoast the a large amount of data to be analyzed was stored on an HDFS~\cite{borthakur2008hdfs} cluster,
%some configuration data was stored on a CVMFS~\cite{blomer2011cernvm} filesystem,
%and a variety of software tools were on an NFS~\cite{howard1988scale},
%PanFS~\cite{welch2008scalable} and AFS~\cite{sandberg1985design} systems. In \emph{Athena} the data and code were available through CVMFS filesystem.

 %\begin{TM} 
%each with a different access method and data source.
%While we knew in advance that it depended upon the large CMSSW distribution,
%it was not apparent until elaborating the script that it depended upon
%two different Github repositories for the Tau source,
%a CVS server at CERN for some configuration information, a public web page
%for the PyYAML library, and the public home page of a Notre Dame student
%for one missing header file.  (The latter is particularly troubling!)
%While, at some level, the authors and users of these software know of these dependencies, they are often missing in
%informal communications or forgotten once the dependency is installed.
%However, once known, they are at least expressed explicitly within the script.
%\end{TM}

%\begin{TM}A much harder problem is that the
%application assumed the presence of many different components in the local
%filesystem view. It would be tempting to capture all of these by simply
%storing a virtual machine image containing the local filesystem. However,
%the application depended on no less than {\bf five} networked filesystems
%available on a particular machine available to the author:
%the data to be analyzed was stored on an HDFS~\cite{borthakur2008hdfs} cluster,
%some configuration data was stored on a CVMFS~\cite{blomer2011cernvm} filesystem,
%and a variety of software tools were on an NFS~\cite{howard1988scale},
%PanFS~\cite{welch2008scalable} and AFS~\cite{sandberg1985design} systems.
%The original authors were not aware of many of these dependencies,
%because they simply relied on local administrators to configure the
%software and make it available.\end{TM}

@@

%If we allow users to work in uncontrolled
%environments, then we must have better methods for understanding the dependencies  of existing programs.  At first, we relied on an expert reader to examine
%the user's script and extract the dependencies.  This is clearly
%not a scalable approach.  We then demonstrated an automated method of observing
%what individual files are accessed by a program. However, this does
%not cover all types of dependencies, particularly those that are networked.
%More sophisticated observation techniques could infer higher-level information,
%such as the RPM package names of the files accessed, the URLs of remote
%repositories named throughout the program, or even the addresses and names of networked dependencies like databases and filesystems.

%\begin{TM}As a means of controlling the complexity
%of dependent software packages, the high energy physics community has developed
%a number of tools that perform run-time configuration and consistency checks
%of the available software. {\tt scram} is the software management tool used
%by the CMS experiment.  Before running any code, {\tt scram} is used to locate
%the appropriate version of software,  set environment variables such as the PATH, run any
%tool-specific configuration, and do the same for all software on which it depends.
%If the correct versions are not available, {\tt scram} halts and emits an error.
%While this procedure has great value for consistency, it also introduces a significant cost
%because it involves a large number of nested scripts traversing a filesystem,
%repeatedly looking up metadata.  In our example, the time to perform this configuration
%with a cold cache is about 14 minutes, which is almost as large as the actual analysis
%run, which takes 20 minutes.\end{TM}

\item {\bf High Selectivity.}  
Although the total size of the resources accessed by HEP
programs is very large, the size of the data and software actually used are much smaller.
Often, an entire repository or data source is named within the script, but the program
only needs a handful of items from that source.  For example, the data is stored on an
HDFS filesystem with 11.6TB of data, but only 18GB are actually consumed by the program. 
%The reason for this great reduction is at first each BEAN event contains a large amount of information, and the TauAnalysis throws away a lot of the irrelevant event information, keeping only the relevant bits.
%The CMSSW repository is 88.1GB in total
%but only 448.3MB of source is checked out, and the actually used software only
%measured 6.3MB.  In a few cases, a source of software is named but never actually accessed.
%(For example, our original script includes the Open Science Grid software stack in the PATH, but does not actually use it.)
%We suspect that end users are accustomed to missing dependencies and thus get in the habit of adding commonly used software,
%whether it is needed or not. 
Thus there is a size tradeoff of capturing dependencies mentioned in the program and dependencies actually used in the program.
A reproducible framework must include robust rules about not including superfluous dependencies, but including unused dependencies that may potentially get used during program execution.

@@

\if 0

\begin{table}
    \centering
    \begin{tabular}{|l|}
        \hline
        {\bf Version 1: Email}\\ \hline
        1. Create a CMS release,\\
            \hspace{9pt} e.g. {\tt cmsrel CMSSW\_5\_3\_11\_patch3} \\
        2. Install the BEAN packages as the instructions: \\
            \hspace{9pt} {\tt \url{https://github.com/cms-ttH/BEAN/blob/...}}\\
        3. Install grid-control: \\ 
            \hspace{9pt} {\tt svn co \url{https://ekptrac.physik.uni-ka/...}} \\
        4. INstall the TauAnalysis package: \\
           \hspace{9pt} {\tt git clone \url{https://github.com/matz-e/...}} \\
           \hspace{9pt} {\tt scram b -j32} \\
        5. Fix grid\_control.cfg and run it. \\
        6. Perform the actual tau roast program. \\ 
        \hline
        {\bf Version 2: Script}\\ \hline
        {\tt setenv CMSSW\_BASE CMSSW\_5\_3\_11\_patch3} \\
        {\tt cmsrel \$HOME/\$CMSSW\_BASE} \\
        {\tt cvs co -r V03-09-23 PhysicsTools/PatUtils} \\
        {\tt git clone \url{https://github.com/cms-ttH/BEAN.git}} \\
        {\tt wget -r \url{http://nd.edu/~abrinke1/...}} \\
        {\tt scram b -j32} \\
        {\tt wget \url{http://pyyaml.org/download/pyyaml/PyYAML...}}\\
        \#the experiment data is from HDFS \\
        {\tt cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10}\\
        {\tt cmsenv}\\
        {\tt python setup.py install --user} \\
        {\tt scripts/roaster data/generic\_ttl.yaml} \\ 
        \hline
        {\bf version 3: Formulated Script} \\ \hline
        {\tt setenv CMSSW\_BASE CMSSW\_5\_3\_11\_patch3} \\
        {\tt setenv {\bf GIT} \url{https://github.com}} \\
        {\tt setenv {\bf PYYAML} \url{http://pyyaml.org}} \\
        {\tt setenv {\bf ND} \url{http://nd.edu}} \\
        {\tt cmsrel \$HOME/\$CMSSW\_BASE} \\
        {\tt cvs co -r V03-09-23 PhysicsTools/PatUtils} \\
        {\tt git clone \${\bf GIT}/cms-ttH/BEAN.git} \\
        {\tt wget -r \${\bf ND}\url{/~abrinke1/ElectronEffectiveArea.h}} \\
        {\tt scram b -j32} \\
        {\tt wget \${\bf PYYAML}/download/pyyaml/PyYAML...}\\
        \#the experiment data is from HDFS \\
        {\tt cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10}\\
        {\tt cmsenv}\\
        {\tt python setup.py install --user} \\
        {\tt scripts/roaster data/generic\_ttl.yaml} \\ 
        \hline
       {\bf Version 4: Fine-Grained Toolkit - Package}\\ \hline
        {\tt setenv CMSSW\_BASE CMSSW\_5\_3\_11\_patch3} \\
        {\tt setenv {\bf GIT} \url{https://github.com}} \\
        {\tt setenv {\bf PYYAML} \url{http://pyyaml.org}} \\
        {\tt setenv {\bf ND} \url{http://nd.edu}} \\
        {\tt cmsrel \$HOME/\$CMSSW\_BASE} \\
        {\tt cvs co -r V03-09-23 PhysicsTools/PatUtils} \\
        {\tt git clone \${\bf GIT}/cms-ttH/BEAN.git} \\
        {\tt wget -r \${\bf ND}\url{/~abrinke1/ElectronEffectiveArea.h}} \\
        {\tt scram b -j32} \\
        {\tt wget \${\bf PYYAML}/download/pyyaml/PyYAML...}\\
        \#the experiment data is from HDFS \\
        {\tt cd \$HOME/\$CMSSW\_BASE/src/PyYAML-3.10}\\
        {\tt cmsenv}\\
        {\tt python setup.py install --user} \\
        {\tt scripts/roaster data/generic\_ttl.yaml} \\ 
        \hline
    \end{tabular}
    \caption{Scripts of each Solution}
    \label{table:scripts}
\end{table}

\fi

>>>>

@@

@@

\item {\bf High Selectivity.}  
Although the total size of the resources accessed by HEP
programs is very large, the size of the data and software actually used are much smaller.
Often, an entire repository or data source is named within the script, but the program
only needs a handful of items from that source.  For example, the data is stored on an
HDFS filesystem with 11.6TB of data, but only 18GB are actually consumed by the program. 
Thus there is a size tradeoff of capturing dependencies mentioned in the program and dependencies actually used in the program.
A reproducible framework must include robust rules about not including superfluous dependencies, but including unused dependencies that may potentially get used during program execution.

@@

### 2015-03-18 paper.tex
Remove unused stuff

\usepackage{comment}
\usepackage{wrapfig}
\excludecomment{TM}
%\setlength{\textwidth}{6.25in}

@@

% \titlerunning{} has to be set to either the main title or its shorter
% version for the running heads. When processed by
% EasyChair, this command is mandatory: a document without \titlerunning
% will be rejected by EasyChair

@@

% A category with the (minimum) three required fields
%\category{H.4}{Information Systems Applications}{Miscellaneous}
%A category including the fourth, optional field follows...
%\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]

%\terms{Theory}

\input {intro}
\input {tauroast}
\input {observation}
\input {evolution}
\input {measure}
\input {evaluation}
%\input {problems}
\input {related_work}
%\input {postscript}
\section{Conclusions and Future work}
In this paper, we propose an invariant framework for conducting reproducible computational science - using light-weight virtualization approaches to preserve applications in the format of self-contained packages and using standardized software delivery mechanisms to deliver and distribute preserved packages.
We use two complex high energy physics applications to illustrate how the framework can help the original authors preserve and distribute the applications, and others reproduce the applications.

@@

\if 0
Section 2: Overview of Application
    CMS/LHC introduction.
    Data sources and reduction of size.
    Code sources and reduction of size.
    Prose observations about the script.
        Uses multiple repos that change over time, with varying level of stability.
        Low selectivity from the larger repos
        Significant initialization time to collect everything.
        Incidental infrastructure tools versus essential objects.
        Some dependencies were surprising.
    Figure: Diagram of app with both code and data sources.
    Table: Show all code and data sources and size within one table.

Section 3: Preservation Strategies
    Figure: Show app in four stages:
        Single email.
        Script with embedded references to dependencies.
        Script with map file that refers to external dependencies.
        Script with map file that refers to preserved dependencies.

    Transform to more suitable format that expresses dependencies.

    Incorporate into archive, saving deps and map file.

    But, how to get the dependencies?

    Three strategies:
        Original - Unmodified application run in original environment.
        Coarse-Grained - Capture deps at large granularity -- whole filesystems and repositories.
        Fine-Grained - Capture deps at a fine granularity -- individual files actually used.

    Coarse-Grained Method (Copy Repositories)
        First, determine dependencies
        Express app as script + map file
        Packaging tool downloads deps, rewrites map file.
        To run packaged application, obtain map, download

    Fine-Trained Toolkit (Parrot)
        Tool to detect dependencies (Parrot)
        Express app as script + map file
        Packaging tool downloads deps, rewrites map file.
        To run package application, run again with Parrot.

Section 4: Evaluation

    Table: Time and size of preserving using each of the two techniques.

    Explain why the techniques show different performance.

    Is one technique more effective than the other?  Why?
\fi

>>>>

\usepackage{comment}
\usepackage{wrapfig}
\excludecomment{TM}

@@

@@

\input {intro}
\input {tauroast}
\input {observation}
\input {evolution}
\input {measure}
\input {evaluation}
\input {related_work}
\section{Conclusions and Future work}
In this paper, we propose an invariant framework for conducting reproducible computational science - using light-weight virtualization approaches to preserve applications in the format of self-contained packages and using standardized software delivery mechanisms to deliver and distribute preserved packages.
We use two complex high energy physics applications to illustrate how the framework can help the original authors preserve and distribute the applications, and others reproduce the applications.

@@

### 2015-03-18 tauroast.tex
Modifications according to the suggestions from reviewers
Remove unused stuff

%The application which is the study of this paper is an CMS application~\cite{collaboration2008cms} called \emph{TauRoast}.
%It searches for cases where the Higgs boson decays to two tau leptons~\cite{chatrchyan2013search}.
%Since the tau leptons are very short-lived, they are not observed directly, but by the particle decay products 
%that they generate.  So, the analysis must search for detector
%events that show a signature of decay products compatible with both hadronic tau and top decays.

Code and data in \emph{TauRoast} is available through five different networked filesystems, namely an HDFS cluster for data files, 
%~\cite{borthakur2008hdfs},~\cite{sandberg1985design},\cite{welch2008scalable}, ~\cite{howard1988scale}
some configuration files were stored on a CVMFS~\cite{blomer2011cernvm} filesystem, and a variety of software tools were on an NFS, PanFS and AFS systems.
In addition, code may exist in version control systems such as Git, CVS, and CMS Software Distribution (CMSSW). %~\cite{cms2006cms}. 
\begin{wrapfigure}{r}{0.4\textwidth}
\small
\centering
\includegraphics[width=.4\textwidth]{data-code-size.eps}
\caption{Inputs to Tau Roast}
\label{fig:data-code-size}
\end{wrapfigure}
Data that is input to \emph{TauRoast} is obtained by reducing it through a pipeline, as shown in Figure \ref{fig:data-code-size}. Consequently, the real input data may 
vary depending upon the science question being researched. Similarly the software may name many possible components but the used components are
smaller than the named ones.

In \emph{Athena} data is obtained through an external Dropbox-like system called the FaxBox, but does not go through any reduction steps. Code is obtained through 
CernVM-FS, which provides the analysis routines. However, depending upon the input data code and the configuration that will be invoked changes. 
Thus in \emph{Athena} the used code and configuration are dynamic depending upon input data, where as in \emph{TauRoast} the code and data are static, 
but the amount of data and code to include changes depending on the involved science.

%In application, code and data that form the applications are drawn from large external repositories through multiple step reductions. 
%Figure \ref{fg:data-code-size} shows the data and code reduction and reliance on software distribution repositories. There are two observations to be 
%derived from 
%of this reduction. First. the actual code contributed by individual groups, in this case the CMS and ATLAS group, is small. 
%But the contributed software relies on several software dependencies, which
%are available software distribution repositories such as the CMS Software Distribution (CMSSW)~\cite{cms2006cms}, and the CVMFS. 
%These repositories contain many different tools, libraries, and utilities, and for ATLAS, the Reco\_TR analysis framework which consists of many analysis routines. 
%
%Figure~\ref{fig:data-code-size} shows that both the code and data
%that form \emph{TauRoast} are drawn from large repositories through
%multiple steps of reduction.  A preservation strategy must weigh
%whether to store the large repositories completely, the fragments
%used by an artifact, or something in between.
%
%{\bf Code Sources.} Like many scientific codes, the central algorithm
%of \emph{TauRoast} is expressed in a relatively small amount of
%custom code developed by the primary author.  But, the code cannot
%run at all without making use of an enormous collection of software
%dependencies.  
%The largest of these repositories is the CMS Software Distribution (CMSSW)~\cite{cms2006cms},
%which contains many different tools, libraries, and utilities.  No single code uses anywhere close to all of these.  But, because it is widely used within the experimental researchers, it is common for users to simply expect that a particular version of the entire repository is available.
% 
%{\bf Data Sources.}
%The CMS collaboration provides end-users with a pre-processed
%and reduced data format, AOD~\cite{holtman2001cms}, 
%which is based on the RAW output of the CMS detector readout electronics and reconstructed world-wide.
%As AOD data are too large to be iteratively processed repetitively in
%a physics analysis workflow, it is normally reduced further in
%structural complexity and content.  For the analysis under
%investigation here, this is a two-step process.  First, the AOD data
%are processed at the Notre Dame working group cluster to BEAN (Boson Exploration Analysis Ntuple) events,
%containing only trivial data containers packed in vectors.  This step
%is time and CPU intensive and its output contains data of 11.6$\,$TB to be
%analyzed by the tau analysis.
%In the second step, the data are reduced to the ``Ntuple'' format,
%which contains only events matching basic quality criteria and
%fields relevant to \emph{TauRoast}.
%Once the data has been reduced to Ntuples, TauRoast can be run as a single
%process, and contains a stringent event selection to look only at high
%quality candidate events for the underlying physical process.
%Quantities from the relevant events can be
%both plotted and used in multivariate analysis to determine the level
%of expected signal in real data.

>>>>

Code and data in \emph{TauRoast} is available through five different networked filesystems, namely an HDFS cluster for data files, 
some configuration files were stored on a CVMFS~\cite{blomer2011cernvm} filesystem, and a variety of software tools were on an NFS, PanFS and AFS systems.
In addition, code may exist in version control systems such as Git, CVS, and CMS Software Distribution (CMSSW). %~\cite{cms2006cms}. 
\begin{wrapfigure}{r}{0.4\textwidth}
\small
\centering
\includegraphics[width=.4\textwidth]{data-code-size.eps}
\caption{Inputs to Tau Roast}
\label{fig:data-code-size}
\end{wrapfigure}
Data that is input to \emph{TauRoast} is obtained by reducing it through a pipeline, as shown in Figure \ref{fig:data-code-size}. Consequently, the real input data may 
vary depending upon the science question being researched. Similarly the software may name many possible components but the used components are
smaller than the named ones.

In \emph{Athena} data is obtained through an external Dropbox-like system called the FaxBox, but does not go through any reduction steps. Code is obtained through 
CVMFS, which provides the analysis routines. However, depending upon the input data code and the configuration that will be invoked changes. 
Thus in \emph{Athena} the used code and configuration are dynamic depending upon input data, where as in \emph{TauRoast} the code and data are static, 
but the amount of data and code to include changes depending on the involved science.
